---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# lens2r


<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)

[![R CMD Check via {tic}](https://github.com/sbalci/lens2r/workflows/R%20CMD%20Check%20via%20{tic}/badge.svg?branch=master)](https://github.com/sbalci/lens2r/actions)
[![Travis build status](https://travis-ci.com/sbalci/lens2r.svg?branch=master)](https://travis-ci.com/sbalci/lens2r)
<!-- badges: end -->

The goal of lens2r is to get Lens.org scholar data into R environment.
You need Lens.org scholar API token to access data, you can [get one here](https://www.lens.org/lens/user/subscriptions#scholar).

> Scholarly Search and Analysis  
Lens serves over 200 million scholarly records, compiled and harmonised from Microsoft Academic, PubMed and Crossref, enhanced with UnPaywall open access information, CORE full text and links to ORCID. The full scholarly citation graph is provided for the first time as an open public resource.



🔬🔬🔬🔬 UNDER CONSTRUCTION 🛠⛔️⚠️🔩


## Installation

<!-- You can install the released version of lens2r from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("lens2r") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sbalci/lens2r")
```


## Examples





```{r example}
library(lens2r)

request <- '{
	"query": {
		"match_phrase": {
			"author.affiliation.name": "Harvard University"
		}
	},
	"size": 1,
	"sort": [{
		"year_published": "desc"
	}]
}'
data <- lens2r::get_scholarly_data(query = request)

output_content <- httr::content(data, "text")

output_flatten <- jsonlite::fromJSON(output_content, flatten = TRUE)

output_flatten_data <- output_flatten$data

output_flatten_data

output_flatten <- as.data.frame(output_flatten)

output_flatten
```





## Similar Works

### lensr

A package to access patent data from the Lens Patent Database
Deprecated

https://github.com/poldham/lensr


### covidlens 

https://github.com/poldham/covidlens

Scientific and Patent Literature on Covid-19 Corona Virus from the Lens for R https://poldham.github.io/covidlens/




### R codes in Lens.org API documentation

https://docs.api.lens.org/samples.html#r

These are the basic codes this package uses

```r
require(httr)
getScholarlyData <- function(token, query){
	url <- 'https://api.lens.org/scholarly/search'
	headers <- c('Authorization' = token, 'Content-Type' = 'application/json')
	httr::POST(url = url, add_headers(.headers=headers), body = query)
}
token <- 'your-access-token'
request <- '{
	"query": {
		"match_phrase": {
			"author.affiliation.name": "Harvard University"
		}
	},
	"size": 1,
	"sort": [{
		"year_published": "desc"
	}]
}'
data <- getScholarlyData(token, request)
content(data, "text")
```



---

<a class="twitter-follow-button" data-show-count="false" href="https://twitter.com/serdarbalci">Follow @serdarbalci</a><script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>  
<a class="bmc-button" target="_blank" href="https://www.buymeacoffee.com/bS0teIs"><img src="https://cdn.buymeacoffee.com/buttons/bmc-new-btn-logo.svg" alt="Buy me a coffee"><span style="margin-left:15px;font-size:28px !important;">Buy me a coffee</span></a>  

https://paypal.me/serdarbalci  

![GitHub followers](https://img.shields.io/github/followers/sbalci?style=social)  
[![Say Thanks!](https://img.shields.io/badge/Say%20Thanks-!-1EAEDB.svg)](https://saythanks.io/to/sbalci) 


---


## Development Status  

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![R CMD Check via {tic}](https://github.com/sbalci/lens2r/workflows/R%20CMD%20Check%20via%20{tic}/badge.svg?branch=master)](https://github.com/sbalci/lens2r/actions)
[![Travis build status](https://travis-ci.com/sbalci/lens2r.svg?branch=master)](https://travis-ci.com/sbalci/lens2r)

